%Clearly state the research problem or question.
%Provide background information to contextualize the research.
%Highlight the significance of the research within the broader field.

%Introduction: An introduction to the topic, including background information, the research question or problem statement, the purpose of the study, and an overview of the paper's organization.
\section{Introduction}

Fallout \autocite{game:fallout1997} is a non-linear sandbox role-playing game for PC and Mac. The game is grounded in a seemingly living world, taking place in a fictitious post-nuclear nightmare scenario for mankind. Survivors give the protagonist missions which tell interconnected stories allowing the player to make deep decisions, leading to new interactions and challenges in the game world. The player will also level up, and PERKS add extra sophistication to the game's rule-set. 

\subsection{Background information}

Fallout, together with many other role-playing games in the 90-s, was commercially successful in America \autocite{sales}. In 1998 it received a sequel, Fallout 2 \autocite{fallout2}. Fallout's producer Tim Cain notes that they wanted to make an open-world game, which today one would call a sandbox game \autocite{cain}. The game has novel video-game design where the player is free to make morally dubious decisions, making the game impactful and relevant to this day.

Game designer Todd Howard reimagined the Fallout games in a popular new series first appearing with Fallout 3 in 2008 \autocite{fallout3}. Fallout 3 became Bethesda's best selling game up to that point. Todd Howard successfully made a game praised for having open-ended gameplay. Fallout 3 is considered to be among the best games ever made, winning the Game Developers Choice Award for Game of the Year 2008 \autocite{award}.

There is also a Fallout television series expected to air in April 2024 \autocite{tvseries}. The television series will be directed by Jonathan Nolan, who co-wrote the superhero films The Dark Knight \autocite{darknight} and The Dark Knight Rises \autocite{darknightrises}, as well as the science-fiction film Interstellar \autocite{interstellar} together with his brother Christopher Nolan. Jonathan's older brother, Christopher Nolan, recently won a BAFTA for Best Direction and a Golden Globe Award for his newest film Oppenheimer \autocite{oppenheimer}. %Adding a bit more detail about the upcoming television series or expanding on Todd Howard's role in reimagining the series could further enrich the discussion.

Role-playing games were a staple of the 90-s \autocite{sales}. The genre has made a comeback with a sequal to the Baldur's Gate series with the highly successful big-budget game Baldur's Gate 3, released more than 20 years after its predecessor \autocite{gate3}. Gary Gigax first popularised role-playing games in the United States with the Dungeons and Dragons tabletop role-playing system, which relies heavily on dice and random numbers \autocite{dnd}. Black Onix popularised the role-playing game genre in Japan \autocite{tetris}.
%Black Onix was designed by Henk Rogers who is also known for securing the rights for Tetris on Gameboy from the Soviet Union for Nintendo.
Later, Steve Jackson tried to remove randomness from role-playing games with his action-based GURPS system \autocite{gurps}. Fallout was originally going to use GURPS before they invented their own SPECIAL role-playing game system \autocite{special}.

\subsection{Purpose of the study}

As role-playing games and sandbox games are important genres in video-game and tabletop gaming, with popular role-playing series such as Final Fantasy, Baldur's Gate, and sandbox games such as Minecraft, there is a need to better understand these games to reproduce their success. The choices presented to players and how the choices interact and influence the game's mechanics and rules will now be examined.
